### 2021-11-09 NSF2021/Description/specificaim2.tex

\subsubsection{Iterative methods for the Allen-Cahn HAP model}
\label{subsec:AC}
In the PIs collaboration, they have developed numerical methods to
solve~\eqref{eq:SL} when $f(u) = u^2$. With this choice of $f(u)$, the
resulting PDE is the linear screened Laplace equation which is
efficiently solved with a double-layer potential representation. For a
more general $f$, such as a double well potential, we will interpret the
solution of~\eqref{eq:SL} as a root finding problem for the operator
\begin{align*}
  F[u] = -\rho \Delta u + f'(u).
\end{align*}

>>>>

\subsubsection{Iterative methods for the Allen-Cahn HAP model}
\label{subsec:AC}
In the PIs collaboration, they have developed numerical methods to
solve~\eqref{eq:SL} when $f(u) = u^2$. With this choice of $f(u)$, the
resulting PDE is the linear screened Laplace equation which is
efficiently solved with a double-layer potential representation. For a
more general $f$, such as a double well potential, we will interpret the
solution of~\eqref{eq:SL} as a root finding problem for the operator
\begin{align*}
  F[u] = -\rho \Delta u + f'(u).
\end{align*}
This non-linear PDE will be solved with Newton's method
\begin{align*}
  u^{N+1} = u^{N} - dF(u^N)^{-1} F(u^N),
\end{align*}
where $dF(u^N) = -\rho \Delta + f''(u^N)$ is the Fr\'{e}chet derivative
of $F$. As expected, the biggest challenge amounts to solving
\begin{align}
  \label{eq:NewtonUpdate}
  - \rho \Delta v + f''(u^{N}) v = F[u^N].
\end{align}
If $f(u)$ is defined in terms of piecewise quadratic equations,
equation~\eqref{eq:NewtonUpdate} is equivalent to
\begin{align*}
  -\rho \Delta v + 
  \left(
  \begin{cases}
    a, &\mbox{if } u^{N}(\xx) \mbox{ closer to $U_1$} \\
    1, &\mbox{if } u^{N}(\xx) \mbox{ closer to $U_0$}
  \end{cases}
  \right)
  v = F[u^N].
\end{align*}
